{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
still update to gpm

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

@@

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBT}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}

>>>>

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

@@

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBT}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}
